Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-26 paper/paper.Rmd
update figure sizes

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="50%", fig.pos="ht"}
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

@@

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="50%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)

@@

```{r block-random, fig.cap="Spatial blocking with option `selection = 'random'`.", out.width="50%", fig.pos="ht"}
resampling_block_random = rsmp("spcv_block", range = 1000, folds = 5)

@@

```{r block-systematic, fig.cap="Spatial blocking with option `selection = 'systematic'`.", out.width="50%", fig.pos="ht"}
resampling_block_systematic = rsmp("spcv_block",
  range = 1000, folds = 5,
  selection = "systematic"
)

@@

```{r coords, fig.cap="Method 'Spatial CV' showing k-means clustering based on coordinates.", out.width="50%", fig.pos="ht"}
resampling_coords = rsmp("spcv_coords", folds = 5)$instantiate(task)

@@

```{r lto, echo=FALSE, out.width="90%", fig.cap="Three-dimensional visualization of method `sptcv\\_cstf` and sub-method Leave-Time-Out (LTO). To support showcasing the temporal grouping, five folds and five temporal levels in variable `Date` were used in this example.", fig.pos="ht"}
knitr::include_graphics("lto.png")
```

@@

```{r llo, echo=FALSE, out.width="90%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-Out' (LLO). To support showcasing the spatial grouping, the viewing angle has been adjusted to a view from top. Points are stacked by temporal levels and only points from the same location are chosen to form a partition.", fig.pos="ht"}
knitr::include_graphics("llo.png")
```

@@

```{r llto, echo=FALSE, out.width="90%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method, i.e. the points which are not used in the training or test set in this fold.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```

@@

```{r custom-cv,  fig.cap="Environmental blocking using a single predictor.", out.width="50%", fig.pos="ht", eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

```{r env-1, fig.cap="Environmental blocking using a single predictor.", out.width="50%", fig.pos="ht"}
resampling_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

@@

```{r env-2, fig.cap="Environmental blocking using multiple predictors.", out.width="50%", fig.pos="ht"}
resampling_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)

>>>>

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

@@

```{r disc, fig.cap="Visualization of 'Leave-one-disc-out' method.", out.width="40%"}
resampling_disc = rsmp("spcv_disc", folds = 5, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)

@@

```{r block-random, fig.cap="Spatial blocking with option `selection = 'random'`.", out.width="40%", fig.pos="ht"}
resampling_block_random = rsmp("spcv_block", range = 1000, folds = 5)

@@

```{r block-systematic, fig.cap="Spatial blocking with option `selection = 'systematic'`.", out.width="40%", fig.pos="ht"}
resampling_block_systematic = rsmp("spcv_block",
  range = 1000, folds = 5,
  selection = "systematic"
)

@@

```{r coords, fig.cap="Method 'Spatial CV' showing k-means clustering based on coordinates.", out.width="40%", fig.pos="ht"}
resampling_coords = rsmp("spcv_coords", folds = 5)$instantiate(task)

@@

```{r lto, echo=FALSE, out.width="70%", fig.cap="Three-dimensional visualization of method `sptcv\\_cstf` and sub-method Leave-Time-Out (LTO). To support showcasing the temporal grouping, five folds and five temporal levels in variable `Date` were used in this example.", fig.pos="ht"}
knitr::include_graphics("lto.png")
```

@@

```{r llo, echo=FALSE, out.width="70%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-Out' (LLO). To support showcasing the spatial grouping, the viewing angle has been adjusted to a view from top. Points are stacked by temporal levels and only points from the same location are chosen to form a partition.", fig.pos="ht"}
knitr::include_graphics("llo.png")
```

@@

```{r llto, echo=FALSE, out.width="70%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method, i.e. the points which are not used in the training or test set in this fold.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```

@@

```{r custom-cv,  fig.cap="Environmental blocking using a single predictor.", out.width="40%", fig.pos="ht", eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

```{r env-1, fig.cap="Environmental blocking using a single predictor.", out.width="40%", fig.pos="ht"}
resampling_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

@@

```{r env-2, fig.cap="Environmental blocking using multiple predictors.", out.width="40%", fig.pos="ht"}
resampling_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)
